---
title: "R Notebook"
author: Urs Klahr
output:
  html_document:
    df_print: paged
---

# Demo-Report: Rolling Stones on Spotify

This is a report about ...
... and some more interesting stuff here 
... and also here.

```{r load_libraries, include=FALSE}
library(dplyr)
library(readr)
 
rs = read_csv("rolling_stones.csv",
              col_types = cols(release_year = col_integer()))
```

```{r}
# get the most popular song title
most_popular_song = rs %>% 
  filter(song_popularity > 0) %>%
  arrange(desc(song_popularity))  %>% 
  head(1) %>%
  select(song_name, song_popularity)  %>% 
  pull(song_name)
```

## most popular song
The most popular song of the Rolling Stones is **"`r most_popular_song`"**.

## list of most popular songs
```{r message=FALSE, warning=FALSE}
rs %>% 
  filter(song_popularity > 0) %>%
  arrange(desc(song_popularity))  %>% 
  head(4) %>%
  select(song_name, song_popularity)
```

## list of least popular songs
```{r message=FALSE, warning=FALSE}
rs %>% 
  filter(song_popularity > 0) %>%
  arrange(desc(song_popularity))  %>% 
  tail(4) %>%
  select(song_name, song_popularity)
```

## Popularity: live vs studio
```{r message=FALSE, warning=FALSE}
rs %>%
  filter(song_popularity > 0) %>%
  group_by(recording = live) %>%
  summarise(popularity = mean(song_popularity))
```



# Header-1
## Header-2
### Header-3
#### Header-4
##### Header-5
###### Header-6

I also generate a plot showing the expenses over the last four
months and show it below.

```{r plot-cars, echo=FALSE}
library(ggplot2)
plot(cars)
```

<image-created-here>

